---
title: "Homework 2"
format: html
editor: visual
---

Problem 1 

The random variable x is binomially-distributed having n = 5 trials and a probability of success p = 0.30. Find the following probabilities.

The probability of x = 0 successes

```{r}
dbinom(0, 5, 0.3)
```


The probability of x = 1 success

```{r}
dbinom(1, 5, 0.3)
```

The probability of x = 2 successes

```{r}
dbinom(2, 5, 0.3)
```

The probability of x = 3 successes

```{r}
dbinom(3, 5, 0.3)
```

The probability of x = 4 successes

```{r}
dbinom(4, 5, 0.3)
```

The probability of x = 5 successes

```{r}
dbinom(5, 5, 0.3)
```

Confirm that the probability of 5 or fewer successes is 1. Use three different
approaches.

```{r}
sum(dbinom(0:5, 5, 0.3))
```
```{r}
dbinom(0, 5, 0.3) + dbinom(1, 5, 0.3) + dbinom(2, 5, 0.3) + dbinom(3, 5, 0.3) + dbinom(4, 5, 0.3) + dbinom(5, 5, 0.3)
```

```{r}
0.16807+0.36015+0.3087+0.1323+0.02835+0.00243
```

Problem 2

North American Airlines (NAA) strictly enforces the baggage weight limit placed on its passengers. Any passenger whose baggage exceeds the weight limit must pay a certain amount per kilogram over that limit. In a recent survey, NAA determined that 20% of its passengers have overweight baggage to check.


Of the next 20 passengers checking in at the NAA ticket counter, what is the probability that exactly four will have overweight baggage?

```{r}
dbinom(4, 20, 0.2)
```


Of the next 20 passengers checking in at the NAA ticket counter, what is the probability that exactly four will have overweight baggage?

```{r}
dbinom(4, 20, 0.2)
```


What is the probability that more than three will have overweight baggage?

```{r}
sum(dbinom(0:3, 20, 0.2))
```

Problem 3

Let x be a Poisson-distributed random variable. Answer the following questions.

When the expected value of the Poisson probability distribution is 1, what is the probability that x will be less than or equal to 2?

```{r}
sum(dpois(0:2, 1))
```


When the expected value of the Poisson probability distribution is 2, what is the probability that x will be less than or equal to 2?

```{r}
sum(dpois(0:2, 2))
```


When the expected value of the Poisson probability distribution is 3, what is the probability that x will be less than or equal to 2?
```{r}
sum(dpois(0:2, 3))
```

Problem 4

A major metropolitan hospital requested 25 emergency room personnel—14 paramedics and 
    11 physicians—to report to work during one of the worst periods of the COVID-19 pandemic.   
     However, because of the restrictions imposed by local authorities on the use of public 
     transportation during this time, five staff members were unable to get from their homes to the 
     hospital in a timely manner.

What is the probability that two of the absent staff were physicians?

```{r}
dhyper(2, 11, 14, 5)
```


What is the probability that two of the absent staff were paramedics?

```{r}
dhyper(2, 14, 11, 5)
```


What is the probability that all the absent staff were paramedics?

```{r}
dhyper(5, 14, 11, 5)
```


What is the probability that none of the absent staff was a paramedic?

```{r}
dhyper(0, 14, 11, 5)
```

