---
title: "Homework 3"
format: html
editor: visual
---

# Problem 1

Let x be the random variable described by the uniform probability distribution with its lower bound at a = −10, upper bound at b = 15.

What is the probability density function, f(x)?

$$ \mu = \frac{a+b}{2} = \frac{-10+15}{2} = 2.5 $$

What is E(x) and σ?

E(x) is the mean which is 2.5

σ is the standard deviation which is $$ \sigma = \sqrt{\frac{b-a^2}{12}} = \sqrt{\frac{(15+10)^2}{12}} = 50.0833 $$


# Problem 2

Referring to the previous exercise, find the following probabilities using the probability 
      density function f(x) and R.

p(5 < x < 10)

```{r}
punif(10, -10, 15) - punif(5, -10, 15)
```


p(-5 < x < 0)

```{r}
punif(0, -10, 15) - punif(-5, -10, 15)
```


p(-5 < x < 5)

```{r}
punif(5, -10, 15) - punif(-5, -10, 15)
```


p(-8 < x < -5)

```{r}
punif(-5, -10, 15) - punif(-8, -10, 15)
```


p(x > 10)

```{r}
(punif(10, -10, 15, lower.tail = FALSE))
```

# Problem 3

3. Let z be the standard normal variable. Use R to answer the following questions.

p(−2  ≤  z  ≤  0.05)

```{r}
pnorm(0.05) - pnorm(-2)
```


p(−1.5  ≤  z  ≤  1.15)

```{r}
pnorm(1.15) - pnorm(-1.5)
```


p(−0.95  ≤  z  ≤  1.96)

```{r}
pnorm(1.96) - pnorm(-0.95)
```


p(−0.10  ≤  z  ≤  2.33)

```{r}
pnorm(2.33) - pnorm(-0.10)
```

# Problem 4

4. Use R to answer the following questions about z.

If the area to the left of z is 0.10, what is z?

```{r}
qnorm(0.10)
```


If the area to the left of z is 0.05, what is z?

```{r}
qnorm(0.05)
```


If the area to the left of z is 0.025, what is z?

```{r}
qnorm(0.025)
```


If the area to the right of z is 0.90, what is z?

```{r}
qnorm(0.90, lower.tail = FALSE)
```


If the area to the right of z is 0.95, what is z?

```{r}
qnorm(0.95, lower.tail = FALSE)
```

# Problem 5


5. If x is a normally-distributed random variable with a mean μ = −91 and standard deviation 
    σ = 6.5, answer the following questions.

What is the probability that x will be greater than -104?

```{r}
pnorm(-104, -91, 6.5, lower.tail = FALSE)
```


What is the probability that x will be greater than -95?

```{r}
pnorm(-95, -91, 6.5, lower.tail = FALSE)
```


What is the probability that x will be greater than -85?

```{r}
pnorm(-85, -91, 6.5, lower.tail = FALSE)
```


What is the probability that x will be less than than -80?

```{r}
pnorm(-80, -91, 6.5)
```


What is the probability that x will be between -100 and -70?

```{r}
pnorm(-70, -91, 6.5) - pnorm(-100, -91, 6.5)
```

# Problem 6

6. A random variable is exponentially-distributed with a mean of μ = 15.

What is the form of the probability density function?

$$f(x)=\frac{1}{15}e^{-\frac{x}{15}}$$

What is the cumulative probability function?

$$p(x \leq x_0)=1-e^{-\frac{x_0}{15}}$$

Find p(x ≤ 3)

```{r}
pexp(3, 1/15)
```

